---
title: "Key outputs preparation"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    number_sections: yes
---
<style>
* {
  font-family: "Palatino"
}

h1{
    font-size: 190%
}

h2{
    font-size: 160%
}

h3{
    font-size: 150%
}

h4{
    font-size: 130%
}

h5{
    font-size: 110%
}

h6{
    font-size: 90%
}
</style>

```{r include=FALSE}
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
library(htmlTable)
library(pander)
library(forcats)
library(kableExtra)
library(readxl)
library(openxlsx)
library(sp)
library(sf)
library(sf)
library(data.table)
library(rgdal)
library(rgeos)
library(htmlTable)
library(janitor)
```

```{r}
options("scipen"=100, "digits"=4)
```

# Load key datasets

```{r}
oct18_M <- read_csv("/Users/nicolas/Documents/R_Git/sind/k_outputs/oct18_M.csv")
```

```{r}
m532 <- read_csv("/Users/nicolas/Documents/R_Git/sind/k_outputs/532.csv")
```

```{r}
buil <- st_read("/Users/nicolas/Documents/R_Git/sind/k_outputs/buildings2043_b.gpkg")
```

# Unique FUC values  and number of roads in each dataset

## oct18_M
```{r}
names(oct18_M)
```

```{r}
oct18_M %>% 
  distinct(`3_Functional_Unit_Co`) %>%
  nrow()
```

```{r}
oct18_M %>% 
  nrow()
```

## m532

```{r}
names(m532)
```

```{r}
m532 %>% 
  distinct(fuc) %>%
  nrow()
```

```{r}
m532 %>% 
  nrow()
```

## Buildngs

```{r}
names(buil)
```

```{r}
buil %>% 
  distinct(FUC) %>%
  nrow()
```

```{r}
buil %>% 
  nrow()
```

# Compare datasets

inner_join()
return all rows from x where there are matching values in y, and all columns from x and y. If there are multiple matches between x and y, all combination of the matches are returned.

## oct18_M values with matching polygon in Buildings2043 by FUC (N=1847)
```{r}
oct18_M %>%
  inner_join(buil, by = c("3_Functional_Unit_Co" = "FUC_d"))
```

## oct18_M values without matching polygon in Buildings2043 by FUC (N=163)
anti_join()
return all rows from x where there are not matching values in y, keeping just columns from x.
```{r}
oct18_M %>%
  anti_join(buil, by = c("3_Functional_Unit_Co" = "FUC_d"))
```

## Buildings2043 polygons with matching values in oct18_M by FUC (N=1847)
```{r}
buil %>%
  inner_join(oct18_M, by = c("FUC_d" = "3_Functional_Unit_Co"))
```

## Buildings2043 polygons without matching values in oct18_M by FUC (N=196)
```{r}
buil %>%
  anti_join(oct18_M, by = c("FUC_d" = "3_Functional_Unit_Co"))
```

## m532 values with matching values in oct18_M by FUC (N=391)
```{r}
m532 %>%
  inner_join(oct18_M, by = c("fuc" = "3_Functional_Unit_Co"))
```

## m532 values with matching polygon in Buildings2043 by FUC (N=385)
```{r}
m532 %>%
  inner_join(buil, by = c("fuc" = "FUC_d"))
```

m435
```{r}
m495 <- st_read("/Users/nicolas/Documents/R_Git/sind/k_outputs/m495.gpkg")
```

```{r}
names(m495)
```

## m532 without spatial representation (lat/lon, FUC) (N=37)
anti_join()
return all rows from x where there are not matching values in y, keeping just columns from x.
```{r}
m37 <-m532 %>%
  anti_join(m495, by = "query_code")
m37
```

```{r}
write.xlsx(m37, file = "m37.xlsx", colNames = TRUE, borders = "rows")
```

# Full join

oct18_M with Buildings2043 (N=2206)
```{r}
fj_ob <- full_join(oct18_M, buil,by = c("3_Functional_Unit_Co" = "FUC_d"))
fj_ob
```

```{r}
names(fj_ob)
```

```{r}
unFUC <- fj_ob %>% 
  distinct(`3_Functional_Unit_Co`) %>%
  pull()
```

```{r}
fj_ob %>% 
  distinct(FUC) %>%
  nrow()
```


```{r}
options(max.print=2500)
```

```{r}
print(unFUC)
```

```{r}
length(unique(unFUC))
```

oct18_M-Buildings2043 (fj_ob) with m532
```{r}
fj_obm <- full_join(fj_ob, m532,by = c("3_Functional_Unit_Co" = "fuc"))
fj_obm
```

```{r}
fj_obm %>% 
  distinct(`3_Functional_Unit_Co`) %>%
  nrow()
```

```{r}
names(fj_obm)
```

```{r}
fj_obm <- st_as_sf(fj_obm)
```

```{r}
class(fj_obm)
```

```{r}
outname <- "oct18_M_FULL.gpkg"
st_write(fj_obm, dsn = outname, layer = "fj_obm", driver = "GPKG" )
```















