---
title: "Data report: OKR"
output:
  html_document:
    df_print: !expr print.me <- function(x, ...) { knitr::asis_output(kableExtra::kbl(x, digits=2, align= 'lr') %>% kable_styling(full_width = F))}
    toc: yes
    toc_depth: '3'
    number_sections: yes
    self_contained: no
---

<!-- https://bookdown.org/yihui/rmarkdown/html-document.html#data-frame-printing -->

```{=html}
<style>
* {font-family: "Trebuchet MS"}h1{font-size: 190%}h2{font-size: 160%}h3{font-size: 150%}h4{font-size: 130%}h5{font-size: 110%}h6{font-size: 90%}
.r code {
    white-space: pre;
}
</style>
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(sf)
library(tmap)
library(mapview)
library(janitor)
library(readr)
library(writexl)
library(data.table)
library(readr)
library(knitr)
library(kableExtra)
```

# Load data

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, 
                      warning=FALSE,
                      results = 'asis')
```

```{r message=FALSE, warning=FALSE, echo = T, results = 'hide'}
# Polygons from Data_report_6.Rmd
p00 <- st_read("/Users/nicolas/Documents/R_GitHub/sind/fP.gpkg")

# points from WMT (Data_report_3.Rmd)
pi00 <- st_read("/Users/nicolas/Documents/R_GitHub/sind/result_feb2021_point.geojson")

# final result spreadsheet downloaded from GD
result <- read_csv("result_feb2021 - 20210406.csv")
```

# Process attributes data

```{r}
result %>%
  rename(FUC = `3_Functional_Unit_Co`) -> result
```

# Summarise attributes data

Size of data frame  
```{r}
dim(result)
```

result_feb2021.csv has 3184 obs. and 142 variables

List of variables  
```{r}
names(result)
```

## Filter by 'premises'

Summary of 'premises'
```{r}
result %>%
  group_by(premises) %>%
  count()
```

Keep Industrial premises

```{r}
result %>%
  filter(premises %in% c("Industrial in mixed use premises", "Industrial in predominantly industrial premises")) -> result1
```

## Summary by FUC

Summary by source (FUC and U_ID)
```{r}
result1 %>%
  group_by(source) %>%
  summarise(Total = n(),
            FUCs = n_distinct(FUC),
            NA_FUCs = sum(is.na(FUC)),
            U_IDs = n_distinct(U_ID)) %>%
  adorn_totals()
```

WMT has 407 industrial variables with unique id (U_ID)
Cities has 1348 industrial records with unique FUC (FUC) - (5 records might be lost)

# Summarise spatial data

## Cities (polygons)

## By FUC

```{r}
p00 %>%
  st_drop_geometry() %>%
  summarise(Total = n(),
            FUCs = n_distinct(FUC),
            NA_FUCs = sum(is.na(FUC))) %>%
  adorn_totals()
```

## WMT (points)

```{r}
pi00 %>%
  st_drop_geometry() %>%
  summarise(Total = n(),
            U_IDs = n_distinct(U_ID),
            NA_U_ID = sum(is.na(U_ID))) %>%
  adorn_totals()
```

```{r}
pi00 %>%
  select(U_ID) -> pi01
```

# Join spatial data with dataframe

## Cities
```{r}
citiesdf <- result1 %>%
  filter(source == "Cities") # 1353 obs.
```

```{r}
p00 %>%
  mutate(FUC = as.numeric(FUC)) %>%
  inner_join(citiesdf, by = ("FUC")) -> p01 # Join data. Retain only rows in both sets.
```


## WMT
```{r}
wmtdf <- result1 %>%
  filter(source == "WMT") # 407 obs.
```

```{r}
pi01 %>%
  st_set_crs(4326) %>%
  st_transform(27700) -> pi01
```

```{r}
# join by U_ID
pi01 %>%
  inner_join(wmtdf, by = ("U_ID")) -> pi02
```

```{r}
sort(pi01$U_ID)
```

```{r}
sort(wmtdf$U_ID)
```

```{r}
sort(setdiff(wmtdf$U_ID, pi01$U_ID))
```

## Find missing POINTS
```{r}
rP <- st_read("/Users/nicolas/Documents/R_GitHub/sind/result_feb2021.gpkg")
```

```{r}
rP %>%
  filter(U_ID %in% setdiff(wmtdf$U_ID, pi01$U_ID)) %>%
  select(Join) %>%
  st_drop_geometry() %>%
  distinct() %>%
  arrange(desc(Join)) -> miP
```

```{r}
# 'Join' already taken
pi02 %>%
  select(Join) %>%
  st_drop_geometry() %>%
  filter(Join %in% miP$Join) -> at
sort(at$Join)
```

```{r}
miP %>%
  filter(!Join %in% at$Join) -> miP
```

```{r}
write_csv(miP, "miP.csv")
```

Load missing points from Dr6
```{r}
miPsf <- st_read("/Users/nicolas/Documents/R_GitHub/sind/miP.gpkg")
```

```{r}
miPsf  %>% 
  filter(!st_is_empty(.)) -> miPsf 
```

```{r}
miPsf
```

```{r}
# join by Join
miPsf %>%
  inner_join(wmtdf, by = ("Join")) -> pi03
```

```{r}
pi02 %>%
  select(-geometry.y) %>%
  rename(geom = geometry.x) -> pi02
```

```{r}
names(pi03)
```


```{r}
pi03 %>%
  select(1:130, 132:143) -> pi03
```

```{r}
rbind(pi02, pi03) -> pi04
```

```{r}
mapview(pi04) + mapview(p01)
```

```{r}
# st_write(p01, "f_cities_pol.gpkg") # 1352 features
# st_write(pi04, "f_wmt_poi.gpkg") # 346 features
```

```{r}
p01 %>%
  st_drop_geometry() %>%
  summarise(Total = n(),
            FUCs = n_distinct(FUC),
            NA_FUCs = sum(is.na(FUC))) %>%
  adorn_totals()
```

```{r}
pi04 %>%
  st_drop_geometry() %>%
  summarise(Total = n(),
            U_IDs = n_distinct(U_ID),
            NA_U_IDs = sum(is.na(U_ID))) %>%
  adorn_totals()
```

