---
title: "Data report: OKR"
output:
  html_document:
    df_print: kable
    toc: yes
    toc_depth: '3'
    number_sections: yes
    self_contained: no
---

<!-- https://bookdown.org/yihui/rmarkdown/html-document.html#data-frame-printing -->

```{=html}
<style>
* {font-family: "Trebuchet MS"}h1{font-size: 190%}h2{font-size: 160%}h3{font-size: 150%}h4{font-size: 130%}h5{font-size: 110%}h6{font-size: 90%}
.r code {
    white-space: pre;
}
</style>
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(sf)
library(tmap)
library(mapview)
library(janitor)
library(readr)
library(writexl)
library(data.table)
library(readr)
library(knitr)
library(kableExtra)
library(concaveman)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, 
                      warning=FALSE,
                      results = 'asis')
options(scipen = 99999)
```

# Reload and compile all Polygon data

+----------------------------------+-----------------------------------+----------------------------------------------------------------------------------------+
| Name                             | Description                       | URL (path)                                                                             |
+==================================+===================================+========================================================================================+
| oct18_N                          | Cities survey results geopackages | <https://drive.google.com/file/d/1VV5nxWja2sA5jbKpHIgdVsE2Ie393QYH/view?usp=sharing>   |
+----------------------------------+-----------------------------------+----------------------------------------------------------------------------------------+
| 200601 New Polygons final upload | New polygons (5 folders)          | <https://drive.google.com/drive/folders/1dVyhXth5rYxvod10N16tDeF_Qvo5I8fz?usp=sharing> |
+----------------------------------+-----------------------------------+----------------------------------------------------------------------------------------+
| Missing Polygons                 | Feb2021 - Missing Polygons        | <https://drive.google.com/drive/u/0/folders/1z6yo7E6avS_3HPTNXO7M6f-q-ePDNhBy>         |
+----------------------------------+-----------------------------------+----------------------------------------------------------------------------------------+

## oct18_N

```{r message=FALSE, warning=FALSE}
oct18 <- st_read("/Users/nicolas/Documents/R_GitHub/sind/oct18_N.gpkg")
```

## 200601 New Polygons final upload

```{r include=FALSE}
zip <- "/Users/nicolas/Documents/R_GitHub/sind/200601 New Polygons final upload-20210218T100648Z-001.zip"
dir <- unzip(zip, junkpaths = TRUE, exdir = tempdir())
dir1 <- subset(dir, grepl(pattern = "\\_b.gpkg$", dir)) # select files end with .gpkg ending "_b"
dir2 <- subset(dir, grepl(pattern = "\\_B.gpkg$", dir)) # select files end with .gpkg ending "_B"
#dir21 <- subset(dir, grepl(pattern = "\\.gpkg$", dir)) # select files end with .gpkg
dir3 <- c(dir1, dir2)
gpkg <- lapply(dir3, st_read, fid_column_name = "fid")
```

```{r include=FALSE}
# remove lists with nrow > 0
gpkg1 <- gpkg[sapply(gpkg, nrow) > 0]
```

```{r include=FALSE}
# create a new variable with CRS
gpkg2 <- lapply(gpkg1, function(x) within(x, crs <- unlist(st_crs(x), recursive = F)))
```

```{r include=FALSE}
# select BNG 
gpkg21 <- rbindlist(gpkg2, use.names=FALSE) %>%
  filter(crs == "OSGB 1936 / British National Grid") %>%
  st_sf() %>%
  select(fid)
```

```{r include=FALSE}
# select WGS 84
gpkg22 <- rbindlist(gpkg2, use.names=FALSE) %>%
  filter(crs == "WGS 84") %>%
  st_sf() %>% 
  st_set_crs(value = 4326) %>%  # assign original projection
  st_transform(27700) %>% # transform to join all
  select(fid)
```

```{r include=FALSE}
# select != BNG | != 4326
gpkg23 <- rbindlist(gpkg2, use.names=FALSE) %>%
  filter(crs != "OSGB 1936 / British National Grid") %>%
  filter(crs != "WGS 84") %>%
  st_sf() %>%
  select(fid)
```

```{r include=FALSE}
npol <- gpkg21 %>%
  rbind(gpkg22)
npol <- npol %>%
  rbind(gpkg23)
```

## Missing Polygons 

```{r }
zip <- "/Users/nicolas/Documents/R_GitHub/sind/Missing Polygons-20210406T082625Z-001.zip"
dir <- unzip(zip, junkpaths = TRUE, exdir = tempdir())
dir1 <- subset(dir, grepl(pattern = "\\_b.gpkg$", dir)) # select files end with .gpkg ending "_b"
dir2 <- subset(dir, grepl(pattern = "\\_B.gpkg$", dir)) # select files end with .gpkg ending "_B"
#dir21 <- subset(dir, grepl(pattern = "\\.gpkg$", dir)) # select files end with .gpkg
dir3 <- c(dir1, dir2)
gpkg <- lapply(dir3, st_read, fid_column_name = "fid")
```

```{r include=FALSE}
# remove lists with nrow > 0
gpkg1 <- gpkg[sapply(gpkg, nrow) > 0]
```

```{r include=FALSE}
# create a new variable with CRS
gpkg2 <- lapply(gpkg1, function(x) within(x, crs <- unlist(st_crs(x), recursive = F)))
```

```{r include=FALSE}
# select BNG 
gpkg21 <- rbindlist(gpkg2, use.names=FALSE) %>%
  filter(crs == "OSGB 1936 / British National Grid") %>%
  st_sf() %>%
  st_transform(27700) %>%
  select(fid)
```

```{r include=FALSE}
# select WGS 84
gpkg22 <- rbindlist(gpkg2, use.names=FALSE) %>%
  filter(crs == "WGS 84") %>%
  st_sf() %>% 
  st_set_crs(value = 4326) %>%  # assign original projection
  st_transform(27700) %>% # transform to join all
  select(fid)
```

```{r include=FALSE}
# select != BNG | != 4326
gpkg23 <- rbindlist(gpkg2, use.names=FALSE) %>%
  filter(crs != "OSGB 1936 / British National Grid") %>%
  filter(crs != "WGS 84") %>%
  st_sf() %>%
  st_transform(27700) %>%
  select(fid)
```

```{r include=FALSE}
mpol <- gpkg21 %>%
  rbind(gpkg22)
mpol <- mpol %>%
  rbind(gpkg23)
```

# Summary of spatial data

## oct18

FUCs
```{r}
oct18 %>%
  st_drop_geometry() %>%
  select(X3_Functional_Unit_Co) %>%
  rename(FUC = X3_Functional_Unit_Co) %>%
  summarise(Total = n(),
            FUCs = n_distinct(FUC),
            NA_FUCs = sum(is.na(FUC))) %>%
  adorn_totals()
```

Some FUCs are duplicated?

```{r}
oct18 %>%
  select(X3_Functional_Unit_Co) %>%
  rename(FUC = X3_Functional_Unit_Co) %>%
  st_drop_geometry() %>%
  group_by(FUC) %>%
  count() %>%
  arrange(desc(n)) %>%
  filter(n > 1) %>%
  adorn_totals()
```

Valid/empty geometries?

```{r}
st_is_empty(oct18) %>%
  length()
```

## npol

FUCs

```{r}
npol %>%
  st_drop_geometry() %>%
  rename(FUC = fid) %>%
  summarise(Total = n(),
            FUCs = n_distinct(FUC),
            NA_FUCs = sum(is.na(FUC))) %>%
  adorn_totals()
```

Valid/empty geometries?

```{r}
st_is_empty(npol) %>%
  length()
```

Some FUCs are duplicated?

```{r}
npol %>%
  st_drop_geometry() %>%
  rename(FUC = fid) %>%
  group_by(FUC) %>%
  count() %>%
  arrange(desc(n)) %>%
  filter(n > 1) %>%
  adorn_totals()
```

## mpol

FUCs

```{r}
mpol %>%
  st_drop_geometry() %>%
  rename(FUC = fid) %>%
  summarise(Total = n(),
            FUCs = n_distinct(FUC),
            NA_FUCs = sum(is.na(FUC))) %>%
  adorn_totals()
```

Valid/empty geometries?

```{r}
st_is_empty(mpol) %>%
  length()
```

Some FUCs are duplicated?

```{r}
mpol %>%
  st_drop_geometry() %>%
  rename(FUC = fid) %>%
  group_by(FUC) %>%
  count() %>%
  arrange(desc(n)) %>%
  filter(n > 1) %>%
  adorn_totals()
```