---
title: "Exploratory Data Analysis"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    number_sections: yes
---
<style>
* {
  font-family: "Palatino"
}

h1{
    font-size: 190%
}

h2{
    font-size: 160%
}

h3{
    font-size: 150%
}

h4{
    font-size: 130%
}

h5{
    font-size: 110%
}

h6{
    font-size: 90%
}
</style>

Exploratory data analysis

<!-- __References__ -->
<!-- - [R for Data Science](https://r4ds.had.co.nz/exploratory-data-analysis.html) -->
<!-- - [Data Wrangling](https://suzan.rbind.io/2018/04/dplyr-tutorial-4/) -->
<!-- - [Data carpentry - nice diagrams](https://datacarpentry.org/R-ecology-lesson/03-dplyr.html) -->
<!-- - [Dplyr tutorial](https://beta.rstudioconnect.com/content/3350/dplyr_tutorial.html) -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
library(openxlsx)
library(htmlTable)
library(pander)
library(forcats)
library(kableExtra)
```

```{r include=FALSE}
form_csv <- read_csv("form-1__sia-audit 2.csv")
```

# Glimpse

```{r}
glimpse(form_csv)
```

# Completeness

Count of NAs per question

```{r}
colSums(is.na(form_csv))
```


```{r warning=FALSE}
form_csv %>%
  group_by(`1_Surveyor_Nickname`) %>%
  summarise_all(funs(sum(is.na(.)))) %>%
  htmlTable(caption="NA count by Question and Surveyor", col.columns = c("none", "#F7F7F7"), css.cell="padding-left:1em; padding-right:1em;", rnames=F, align = "lr")
```

# Classes 'Activity' and 'SIC' codes

__"1.2 Description of organisations activity"__

```{r}
descr_class <- form_csv %>%
  group_by(`6_12_Description_of_`) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 
```

```{r}
descr_class %>%
  head(35) %>%
  htmlTable(caption="1.2 Description of organisations activity (top 35)", col.columns = c("none", "#F7F7F7"), css.cell="padding-left:1em; padding-right:1em;", rnames=F, align = "lr")
```

Unique values in "1.2 Description of organisations activity"
```{r}
form_csv %>% 
  distinct(`6_12_Description_of_`) %>%
  nrow()
```

One of a kind values in "1.2 Description of organisations activity" (top 5)
```{r}
descr_class %>%
  group_by(n) %>%
  summarise(kind = n()) %>%
  head(5) %>%
  rename("Number of species" = n, "Count" = kind) %>%
  pander()
```


```{r eval=FALSE, include=FALSE}
write.xlsx(descr_class, file = "/Users/nicolas/Documents/R_Github2/sind/descr_class.xlsx", colNames = TRUE, borders = "rows")
```

Download full [1.2 Description of organisations activity](https://github.com/npalomin/sind/blob/master/descr_class.xlsx) table

__"7.4 SIC Code"__

```{r}
SIC_class <- form_csv %>%
  group_by(`74_74_SIC_Code`) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 
```

```{r}
SIC_class %>%
  head(35) %>%
  htmlTable(caption="7.4 SIC Code (top 35)", col.columns = c("none", "#F7F7F7"), css.cell="padding-left:1em; padding-right:1em;", rnames=F, align = "lr")
```

Unique values in "7.4 SIC Code"
```{r}
form_csv %>% 
  distinct(`74_74_SIC_Code`) %>%
  nrow()
```

```{r eval=FALSE, include=FALSE}
write.xlsx(SIC_class, file = "/Users/nicolas/Documents/R_Github2/sind/SIC_class.xlsx", colNames = TRUE, borders = "rows")
```

Download full [7.4 SIC Code](https://github.com/npalomin/sind/blob/master/SIC_class.xlsx) table
