---
title: "Exploratory Data Analysis"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    number_sections: yes
---
<style>
* {
  font-family: "Palatino"
}

h1{
    font-size: 190%
}

h2{
    font-size: 160%
}

h3{
    font-size: 150%
}

h4{
    font-size: 130%
}

h5{
    font-size: 110%
}

h6{
    font-size: 90%
}
</style>

Exploratory data analysis

<!-- __References__ -->
<!-- - [R for Data Science](https://r4ds.had.co.nz/exploratory-data-analysis.html) -->
<!-- - [Data Wrangling](https://suzan.rbind.io/2018/04/dplyr-tutorial-4/) -->
<!-- - [Data carpentry - nice diagrams](https://datacarpentry.org/R-ecology-lesson/03-dplyr.html) -->
<!-- - [Dplyr tutorial](https://beta.rstudioconnect.com/content/3350/dplyr_tutorial.html) -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(sf)
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
library(htmlTable)
library(pander)
library(forcats)
library(kableExtra)
#install.packages(c("readxl","writexl")) 
library(readxl)
library(writexl)
```

```{r include=FALSE}
form_csv <- read_csv("form-1__sia-audit.csv")
```

```{r}
oct10 <- read.csv("/Users/nicolas/Documents/SIND_local_CASA/epi_data_downloads_temp/form-1__sia-audit.csv")
```

```{r eval=FALSE, include=FALSE}
write.xlsx(oct10, file = "/Users/nicolas/Documents/SIND_local_CASA/epi_data_downloads_temp/oct10.xlsx", colNames = TRUE, borders = "rows")
```

```{r include=FALSE}
# finalDB <- read_csv("/Users/nicolaspalominos/Desktop/form-1__sia-audit.csv")
```

```{r eval=FALSE, include=FALSE}
write.xlsx(finalDB, file = "/Users/nicolaspalominos/Desktop/finalDB.xlsx", colNames = TRUE, borders = "rows")
```




# Glimpse

```{r}
glimpse(form_csv)
```

# Completeness

Count of NAs per question

```{r}
colSums(is.na(form_csv))
```


```{r warning=FALSE}
form_csv %>%
  group_by(`1_Surveyor_Nickname`) %>%
  summarise_all(funs(sum(is.na(.)))) %>%
  htmlTable(caption="NA count by Question and Surveyor", col.columns = c("none", "#F7F7F7"), css.cell="padding-left:1em; padding-right:1em;", rnames=F, align = "lr")
```

# Classes 'Activity' and 'SIC' codes

__"1.2 Description of organisations activity"__

```{r}
descr_class <- form_csv %>%
  group_by(`6_12_Description_of_`) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 
```

```{r}
descr_class %>%
  head(35) %>%
  htmlTable(caption="1.2 Description of organisations activity (top 35)", col.columns = c("none", "#F7F7F7"), css.cell="padding-left:1em; padding-right:1em;", rnames=F, align = "lr")
```

Unique values in "1.2 Description of organisations activity"
```{r}
form_csv %>% 
  distinct(`6_12_Description_of_`) %>%
  nrow()
```

One of a kind values in "1.2 Description of organisations activity" (top 5)
```{r}
descr_class %>%
  group_by(n) %>%
  summarise(kind = n()) %>%
  head(5) %>%
  rename("Number of species" = n, "Count" = kind) %>%
  pander()
```


```{r eval=FALSE, include=FALSE}
write.xlsx(descr_class, file = "/Users/nicolas/Documents/R_Github2/sind/descr_class.xlsx", colNames = TRUE, borders = "rows")
```

Download full [1.2 Description of organisations activity](https://github.com/npalomin/sind/blob/master/descr_class.xlsx) table

__"7.4 SIC Code"__

```{r}
SIC_class <- form_csv %>%
  group_by(`74_74_SIC_Code`) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 
```

```{r}
SIC_class %>%
  head(35) %>%
  htmlTable(caption="7.4 SIC Code (top 35)", col.columns = c("none", "#F7F7F7"), css.cell="padding-left:1em; padding-right:1em;", rnames=F, align = "lr")
```

Unique values in "7.4 SIC Code"
```{r}
form_csv %>% 
  distinct(`74_74_SIC_Code`) %>%
  nrow()
```

```{r eval=FALSE, include=FALSE}
write.xlsx(SIC_class, file = "/Users/nicolas/Documents/R_Github2/sind/SIC_class.xlsx", colNames = TRUE, borders = "rows")
```

Download full [7.4 SIC Code](https://github.com/npalomin/sind/blob/master/SIC_class.xlsx) table

```{r}
form_csv %>%
  group_by(`19_31_Floor_levels_t`) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 
```


Q3
```{r}
dupFUC <- finalDB %>%
  group_by(`3_Functional_Unit_Co`) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 
```

```{r eval=FALSE, include=FALSE}
write.xlsx(dupFUC, file = "/Users/nicolaspalominos/Desktop/dupFUC.xlsx", colNames = TRUE, borders = "rows")
```

```{r}
descr_classDB <- form_csv %>%
  group_by(`6_12_Description_of_`) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 
```

Q4
```{r}
form_csv %>%
  group_by(`20_32_How_many_store`) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 
```

```{r}
options("scipen"=100, "digits"=4)
```

```{r}
descr_na <- form_csv %>%
  group_by(`3_Functional_Unit_Co`) %>%
  subset(is.na(`6_12_Description_of_`))
  
```

```{r}
write.xlsx(descr_na, file = "descr_na.xlsx", colNames = TRUE, borders = "rows")
```


CASE WHEN   "f_19_31_Floor_levels_t" LIKE '%Basement%' THEN 1
ELSE 0
END

```{r}
missingFUC %>%
  group_by(`1_Surveyor_Nickname`) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
```


Combine two spreadsheets oct10 and oct18

```{r}
# library(readxl)
# oct10 <- read_excel("~/Documents/SIA/oct10.xlsx")
# View(oct10)
```

```{r}
names(oct10)
```

```{r}
names(oct18)
```

```{r}
str(oct18)
```

```{r}
oct10_1 <- oct10 %>%
  select(-c(created_at, created_by))
```

```{r}
oct18r <- oct18 %>%
  `colnames<-`(c(1:73))
```

```{r}
oct10_1r <- oct10_1 %>%
  `colnames<-`(c(1:73))
```

```{r}
names(oct10_1r)
```

```{r}
str(oct10_1r)
```

```{r}
oct10_1r <- oct10_1r %>%
  mutate_at("23", as.numeric)
```


-----

```{r}
uno <- union(oct10_1r, oct18r)
```

```{r}
uno <- uno %>%
  drop_na(`7`)
```

```{r}
names <- names(oct18)[c(1:64,66:69,71:73)]
```

```{r}
uno <- uno %>%
  select(-65,-70) %>%
  distinct() %>%
  `colnames<-`(names)
```

```{r}
write_xlsx(uno,"merge.xlsx", col_names = T)
```

```{r}
library(readxl)
D_RS <- read_excel("~/Documents/SIA/Organisation Description_RS.xlsx")
```

```{r}
names(D_RS)
```

## Final Summary

```{r}
ds154 <- st_read("/Users/nicolas/Documents/SINDA_local/Final_data_from_gd/Cleaned_154_full.gpkg")
```

```{r}
#install.packages("skimr")
library(skimr)
```


```{r}
sumta <- skim(ds154) %>%
  as.tibble() %>%
  select(2,3,11,12) %>%
  rename(variable = skim_variable)
sumta
```

```{r}
write_xlsx(sumta,"sumta.xlsx", col_names = T)
```

```{r}
oct18N <- st_read("/Users/nicolas/Documents/SINDA_local/Final_data_from_gd/oct18_N.gpkg")
```

```{r}
# Common column names
cols <- intersect(colnames(ds154), colnames(oct18N))
cols
```

```{r}
# replace names programatically
# Use purrr::set_names() with annonymous function of stringr operations
df1 <- ds154 %>%
  set_names(~ str_to_lower(.) %>% 
              str_replace_all("x_", ""))
```

```{r}
df2 <- oct18N %>%
  set_names(~ str_to_lower(.) %>% 
              str_replace_all("x", ""))
```

```{r}
# Common column names
cols <- intersect(colnames(df1), colnames(df2))
cols
```

```{r}
# convert 'created at' to factor
df2 <- df2 %>%
  mutate_at(vars(created_at),list(factor))
```

```{r}
# bind with data table
library(data.table)
```

```{r}
# make named list
l <- list(df1 = df1 , df2 = df2)
dff <- rbindlist( l, use.names = TRUE, fill = TRUE, idcol = "origin" )
```

```{r}
dffsf <- dff %>%
  st_as_sf()
```

```{r}
colnames(dffsf)
```

```{r}
# compare columns 'fuc' with 'fuc_s'
dins <- dffsf %>%
  select(83,84,86,114) %>%
  mutate(TEST = as.character(fuc == fuc_s))
# keep 'fuc_s'
```

```{r}
# summary
dffsf %>%
  select(-83) %>%
  skim() %>%
  as.tibble()
# 2043 factor.n.unique fuc_s
```

```{r}
dffsf <- dffsf %>%
  add_count(fuc_s)
```

```{r}
dffsf %>%
  filter(n == 2) %>%
  select(fuc_s, n, mb_comment, action_spatial, action_spreadsheet)
```

```{r}
dffsf <- dffsf %>%
  rename(id = fid)
```

```{r}
#st_write(dffsf,"/Users/nicolas/Documents/SINDA_local/Final_data_from_gd/oct2020.gpkg")
```

```{r}
oct2020 <- st_read("/Users/nicolas/Documents/SINDA_local/Final_data_from_gd/oct2020.gpkg")
```

```{r}
colnames(oct2020)
```

```{r}
# summary
oct2020 %>%
  select(-83) %>%
  skim() %>%
  as.tibble() %>%
  arrange(desc(complete_rate))
```

```{r}
df3 <- oct2020 %>%
  mutate(desc_org = X6_12_description_of_) %>%
  select(-83) %>%
  mutate(`desc_org` = recode(`desc_org`,
                                                    "Vacant" = "vacant",
                                                    "Residential" = "residential",
                                                    "unidentified" = "unidentifiable",
                                                    "Unidentifiable" = "unidentifiable",
                                                    "Demolished" = "demolished",
                                                    "demolished / vacant" = "demolished",
                                                    "Derelict" = "derelict",
                                                    "Development" = "development",
                                                    "Under development" = "development",
                                                    "vehicle repair" = "Vehicle repair",
                                                    "Vehicle Repairs" = "Vehicle repair",
                                                    "Vehicle Repair and Service" = "Vehicle repair",
                                                    "Vehicle services and repairs" = "Vehicle repair",
                                                    "Vehicle Repairs & Servicing" = "Vehicle repair",
                                                    "Vehicle Repairs and Servicing" = "Vehicle repair",
                                                    "Vehicle repairs" = "Vehicle repair",
                                                    "Car servicing" = "Vehicle repair",
                                                    "Car repair" = "Vehicle repair",
                                                    "Car repairs" = "Vehicle repair",
                                                    "Car mechanic" = "Vehicle repair",
                                                    "Car Mechanic" = "Vehicle repair",
                                                    "Vehicle services" = "Vehicle repair",
                                                    "Car repair and Maintenance" = "Vehicle repair",
                                                    "Car service, repair" = "Vehicle repair",
                                                    "Car service, repair, conversion" = "Vehicle repair",
                                                    "Car service, repair; tyre sales and fitting" = "Vehicle repair",
                                                    "Car mechanics, MOT check" = "Vehicle repair",
                                                    "Car service, repairs" = "Vehicle repair",
                                                    "Car services" = "Vehicle repair",
                                                    "Automobile Engineer" = "Vehicle repair",
                                                    "artist" = "Artist studio",
                                                    "Artists" = "Artist studio",
                                                    "Artist" = "Artist studio",
                                                    "Artistic creation" = "Artist studio",
                                                    "Artists studios" = "Artist studio",
                                                    "Artist / painter" = "Artist studio",
                                                    "Artist Studio" = "Artist studio",
                                                    "Artisit, Ceramist" = "Artist studio",
                                                    "Artist / landscape painter" = "Artist studio",
                                                    "Artist and Ceramist" = "Artist studio",
                                                    "Artist and furniture maker" = "Artist studio",
                                                    "Artist studio in live/work unit" = "Artist studio",
                                                    "Artist studio, printmaking" = "Artist studio",
                                                    "Artist studio/workshop" = "Artist studio",
                                                    "Artist Studios" = "Artist studio",
                                                    "Artist, Illustrator" = "Artist studio",
                                                    "Artists/Furniture manufacturers" = "Artist studio",
                                                    "restaurant" = "Restaurant",
                                                    "Restaurants" = "Restaurant",
                                                    "Architecture" = "Architecture practice",
                                                    "Architecture design" = "Architecture practice",
                                                    "Architectural practice" = "Architecture practice",
                                                    "Architectural Practice" = "Architecture practice",
                                                    "Interior and Architecture design" = "Architecture practice",
                                                    "Architect" = "Architecture practice",
                                                    "Architectrual Consultants" = "Architecture practice",
                                                    "Architects" = "Architecture practice",
                                                    "Architecture & Interior Design" = "Architecture practice",
                                                    "Architecture and interior designers" = "Architecture practice",
                                                    "Architecture office" = "Architecture practice",
                                                    "Architecure Practice" = "Architecture practice",
                                                    "Non Industrial" = "Non industrial",
                                                    "Photographer" = "Photography studio",
                                                    "Photography" = "Photography studio",
                                                    "Photography Studio" = "Photography studio",
                                                    "Advertising photography" = "Photography studio",
                                                    "Ceramics" = "Ceramist",
                                                    "Ceramic sculpture" = "Ceramist",
                                                    "Ceramics, fine art" = "Ceramist",
                                                    "Ceramics, pottery" = "Ceramist",
                                                    "Ceramics: sculpture, tableware" = "Ceramist",
                                                    "Ceramics Design and manufacture" = "Ceramist",
                                                    "Ceramics and sculpture" = "Ceramist",
                                                    "Ceramic artist" = "Ceramist",
                                                    "Ceramic studio" = "Ceramist",
                                                    "Fine art ceramics" = "Fine art",
                                                    "Fine art, painting" = "Fine art",
                                                    "Fine art, sculpture" = "Fine art",
                                                    "Graphic Design" = "Graphic design",
                                                    "Graphic designers" = "Graphic design",
                                                    "offices" = "Offices",
                                                    "Office block" = "Offices",
                                                    "Adult education" = "Adult learning centre", 
                                                    "Adult education centre" = "Adult learning centre",
                                                    "Adult education Learning" = "Adult learning centre",
                                                    "Adult Learning Centre" = "Adult learning centre",
                                                    "Bicycle Repairs, Servicing & Sales" = "Bicycle service",
                                                    "Bicycle service, repair; parts sales" = "Bicycle service",
                                                    "Bike repair" = "Bicycle service",
                                                    "Bike Repairs and Servicing" = "Bicycle service",
                                                    "Bike Sales, Servicing & Repairs" = "Bicycle service",
                                                    "Car Wash" = "Car wash",
                                                    "Car wash / valeting" = "Car wash",
                                                    "Car wash, valeting" = "Car wash",
                                                    "Car washing" = "Car wash",
                                                    "Carwash" = "Car wash"
                                                    ))
```

```{r}
df3 %>%
  skim() %>%
  as.tibble() %>%
  arrange(desc(complete_rate))
```

```{r}
#library(stringr)
df4 <- df3 %>%
  mutate(class = word(desc_org, 1)) %>%
  mutate_at(vars(class), list(toupper)) %>%
  mutate_at(vars(class), list(factor)) %>%
  add_count(class, name = "n_class") %>%
  mutate(class1 = case_when(is.na(class) ~ "no_info",
                            class == "VACANT" ~ "vacant",
                            class == "RESIDENTIAL" ~ "residential",
                            class == "ARTIST" ~ "artist",
                            class == "UNIDENTIFIABLE" ~ "unidentifiable",
                            class == "DEMOLISHED" ~ "demolished",
                            class == "VEHICLE" ~ "vehicle",
                            class == "ARCHITECTURE" ~ "architecture",
                            class == "DERELICT" ~ "derelict",
                            class == "STORAGE" ~ "storage",
                            TRUE ~ "other"))
```

```{r}
df4 %>%
  skim() %>%
  as.tibble() %>%
  arrange(desc(complete_rate))
```

```{r}
df4%>%
  group_by(class) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
```

```{r}
st_write(df4,"/Users/nicolas/Documents/SINDA_local/Final_data_from_gd/oct2020_v0.gpkg", append=FALSE)
```

```{r}
df4 %>% filter(fuc_s == 303)
```

```{r}
df5 <- df4 %>%
  as.data.frame()
```

```{r}
write_xlsx(df5,"/Users/nicolas/Documents/SINDA_local/Final_data_from_gd/oct2020_v0.xlsx", col_names = T)
```

```{r}
form_csv <- read_csv("/Users/nicolas/Downloads/form-1__sia-audit.csv")
```

```{r}
colnames(form_csv)
```

```{r}
df4 %>%
  select(class, class1)
```

