---
title: "leaflet-webapp"
output: 
  html_document:
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(sf)
library(readr)
library(mapview)
library(tidyverse)
library(ggthemes)
library(webshot)
library(leaflet)
library(leafgl)
library(leaflet.extras)
library(htmlwidgets)
library(RColorBrewer)
library(here)
#install.packages("skimr")
#install.packages("pillar")
#install.packages("dplyr")
library(pillar)
library(skimr)
library(janitor)
library(unikn)
library(tmap)
```

```{r}
geom <- st_read(here("2022/data/survey-results.gpkg"))
#geomg <- st_read(here("2022/data/survey-results.geojson"))
bound <- st_read(here("2022/data/southwark-boundary.gpkg"))
ipol <- st_read("/Users/nicolas/Documents/R_GitHub/sind/QGIS/data/dataSouthwark/proc-cleaned/industrial-planning-polygons.gpkg")

sf_use_s2(FALSE)
```

```{r}
ipol %>%
  mutate(Planning_info = case_when(is.na(Name) ~ LSIS,
                                   TRUE ~ Name)) -> ipol1

ipol1 %>%
  mutate(Planning_info = case_when(is.na(Planning_info) ~ Address,
                                   TRUE ~ Planning_info),
         layer = case_when(layer == "LSIS" ~ "Locally Significant Industrial Site",
                           layer == "NSPSPIL" ~ "NSP Strategic Protected Industrial Land",
                           layer == "PILL" ~ "Preferred Industrial Location Local",
                           layer == "PILS" ~ "Preferred Industrial Location Strategic",
                           layer == "SPA" ~ "Southwark Planning Application")) -> ipol2

ipol2 %>%
  #st_drop_geometry() %>%
  select(Planning_info, layer) %>%
  rename(Layer = layer) -> ipol3
ipol3

#st_write(ipol3, here("2022/Data/industrial-planning-polygons.gpkg"))
```


```{r}
geom %>%
  filter(!is.na(Sector)) %>%
  filter(!is.na(Manufacturing.making)) -> geom1
```

```{r}
skim(geom1)
```


# Interactive map
```{r}
url_map <- "https://api.mapbox.com/styles/v1/npalomin/ckkfbcl5622tv17rzxz1lpt33/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoibnBhbG9taW4iLCJhIjoiY2owMDF5YXQxMDA2eDMybmwwd2tqYTU3bSJ9.Icvrku6Q57o8L0gncJI89g"

# sector
colorRampPalette(brewer.pal(8, "Set1"))(10) -> pal10
#seecol(pal10, hex=TRUE)

# palette sector
paletteS <- colorFactor(palette = pal10, levels = sort(unique(geom1$Sector)))

# palette manufacturing
paletteM <- colorFactor(palette = c("grey60", "#E41A1C"),
                        levels = unique(geom1$Manufacturing.making), na.color = "transparent")

# palette Repair
paletteR <- colorFactor(palette = c("grey60", "#658E67"),
                        levels = unique(geom1$Repair), na.color = "transparent")

# palette Creative industrial
paletteC <- colorFactor(palette = c("grey60", "#824273"),
                        levels = unique(geom1$Creative.industrial), na.color = "transparent")

# palette Creative industrial
paletteB <- colorFactor(palette = c("grey60", "#c6610a"),
                        levels = unique(geom1$Building.construction.repair), na.color = "transparent")

# palette Creative industrial
paletteW <- colorFactor(palette = c("grey60", "#ec53a4"),
                        levels = unique(geom1$Wholesale.distribution), na.color = "transparent")



#seecol(paletteM(unique(geom1$Manufacturing.making)))
#seecol(c("#E41A1C","#658E67","#824273","#c6610a","#ec53a4"))
```

ref: https://rstudio.github.io/leaflet/colors.html
ref: file:///Users/nicolas/Documents/R_GitHub/BGS/2bu_2ye.html
ref: https://github.com/npalomin/BGS/blob/main/Data_preparation.Rmd
ref: file:///Users/nicolas/Documents/R_GitHub/urbandp/shiny_test/Exploratory.html

```{r message=FALSE, warning=FALSE}
bound %>%
  st_transform(4326) -> bound4

# create grid
bound %>%
  st_transform(3857) %>%
  # approx to 500m
  st_make_grid(., 782) %>%
  st_transform(4326) %>%
  st_intersection(bound4) -> grid

bound %>%
  st_transform(3857) %>%
  # approx to 500m
  st_make_grid(., 782, what = "corners") %>%
  st_transform(4326) %>%
  st_intersection(bound4) %>%
  st_as_sf() -> grid2

grid2 %>%
  st_transform(27700) %>%
  st_cast("MULTIPOINT") %>%
  st_buffer(., dist = 20) -> corners

grid %>%
  st_cast("LINESTRING") %>%
  st_transform(27700) %>%
  st_intersection(corners) %>%
  st_transform(4326) -> grid3
```

```{r}
grid2 %>%
  st_transform(27700) %>%
  st_cast("MULTIPOINT") %>%
  st_buffer(., dist = 20) %>%
  plot()
```


```{r}
bound4
ipol3 %>%
  st_transform(4326) -> ipol3

leaflet() %>%
  addTiles(urlTemplate = url_map, group = "Map") %>%
  addProviderTiles(providers$CartoDB.Positron, group = "Light") %>%
  # boundary
  addPolylines(data = bound4,
              color = "#bfaabf",
              weight = 2) %>%
  addPolylines(data = grid,
              color = "#bfaabf",
              weight = 0.5) %>%
  addPolylines(data = grid3,
              color = "#bfaabf",
              weight = 1.1) %>%
  addPolylines(data = ipol3,
              color = "#3aa9ab",
              weight = 3,
              opacity = 0.2,
              fill = TRUE,
              fillColor = "#3aa9ab",
              fillOpacity = 0.01,
              #dashArray = "3",
              label = paste(ipol3$Planning_info, "<br/>", ipol3$Layer, 
                            sep="") %>% lapply(htmltools::HTML),
              group = "Industrial Planning",
              highlightOptions = highlightOptions(fillOpacity = 0.2, weight = 1, opacity = 1, color = "yellow", bringToFront = TRUE, sendToBack = TRUE)) %>%
  addScaleBar()

#mapview(bound4)
```


```{r message=FALSE, warning=FALSE}
geom1 %>%
  st_transform(4326) %>%
  leaflet() %>%
  addTiles(urlTemplate = url_map, group = "Satellite") %>%
  addProviderTiles(providers$CartoDB.Positron, group = "Street") %>%
  setView(lng = -0.076, lat = 51.488, zoom = 15) %>%
  addScaleBar("bottomleft", options = scaleBarOptions(metric = TRUE)) %>%
  # boundary & grid
  addPolylines(data = bound4,
              color = "#bfaabf",
              weight = 3) %>%
  addPolylines(data = grid,
              color = "#bfaabf",
              weight = 0.5) %>%
  addPolylines(data = grid3,
              color = "#bfaabf",
              weight = 1.1) %>%
  # sector
  addPolygons(color = ~paletteS(Sector),
              fillColor = ~paletteS(Sector),
              stroke = TRUE,
              weight = 1,
              opacity = 1,
              fillOpacity = 0.8,
              label = paste(
                "Name: ", geom1$Name.of.organis, "<br/>",
                "Sector: ", geom1$Sector, "<br/>",
                "Category: ", geom1$Category.plus, "<br/>",
                "Premises type: ", geom1$Premises, "<br/>",
                "Address: ", paste0(geom1$Street.name.eg, " ", geom1$Street.number), "<br/>",
                "<img src='https://maps.googleapis.com/maps/api/streetview?size=640x640&location=", geom1$coordy, ",", geom1$coordx, "&heading=", geom1$heading, "&pitch=1&key=AIzaSyC-v_x-RZvp_a545Q-XCRf_NGwEo9X7mBI&width=320' width=\"300\">",
                sep="") %>% lapply(htmltools::HTML),
              group = "Sector",
              highlightOptions = highlightOptions(fillOpacity = 0.75, weight = 1, opacity = 1, color = "yellow", bringToFront = TRUE, sendToBack = TRUE)) %>%
  addLegend(colors = pal10, labels = sort(unique(geom1$Sector)), group = "Sector", title = "Sector", opacity = 1,
            position = "bottomright") %>%
  # manufacturing
  addPolygons(color = ~paletteM(Manufacturing.making),
              fillColor = ~paletteM(Manufacturing.making),
              stroke = TRUE,
              weight = 1,
              opacity = 1,
              fillOpacity = 0.8,
              group = "Manufacturing",
              label = paste(
                "Name: ", geom1$Name.of.organis, "<br/>",
                "Sector: ", geom1$Sector, "<br/>",
                "Category: ", geom1$Category.plus, "<br/>",
                "Manufacturing/Making: ", geom1$Manufacturing.making,
                sep="") %>% lapply(htmltools::HTML),
              highlightOptions = highlightOptions(fillOpacity = 0.75, weight = 1, opacity = 1, color = "yellow", bringToFront = TRUE, sendToBack = TRUE)) %>%
  addLegend(colors = rev(colorRampPalette(brewer.pal(9, "Set1"))(2)),
            labels = unique(geom1$Manufacturing.making), group = "Manufacturing", opacity = 1,
            title = "Manufacturing/Making",
            position = "bottomright") %>%
  # repair
  addPolygons(color = ~paletteR(Repair),
              fillColor = ~paletteR(Repair),
              stroke = TRUE,
              weight = 1,
              opacity = 1,
              fillOpacity = 0.8,
              group = "Repair",
              label = paste(
                "Name: ", geom1$Name.of.organis, "<br/>",
                "Sector: ", geom1$Sector, "<br/>",
                "Category: ", geom1$Category.plus, "<br/>",
                "Repair: ", geom1$Repair,
                sep="") %>% lapply(htmltools::HTML),
              highlightOptions = highlightOptions(fillOpacity = 0.75, weight = 1, opacity = 1, color = "yellow", bringToFront = TRUE, sendToBack = TRUE)) %>%
  addLegend(colors = c("grey60", "#658E67"),
            labels = unique(geom1$Repair), group = "Repair", opacity = 1,
            title = "Repair",
            position = "bottomright") %>%
  # creative
  addPolygons(color = ~paletteC(Creative.industrial),
              fillColor = ~paletteC(Creative.industrial),
              stroke = TRUE,
              weight = 1,
              opacity = 1,
              fillOpacity = 0.8,
              group = "Creative",
              label = paste(
                "Name: ", geom1$Name.of.organis, "<br/>",
                "Sector: ", geom1$Sector, "<br/>",
                "Category: ", geom1$Category.plus, "<br/>",
                "Creative: ", geom1$Creative.industrial,
                sep="") %>% lapply(htmltools::HTML),
              highlightOptions = highlightOptions(fillOpacity = 0.75, weight = 1, opacity = 1, color = "yellow", bringToFront = TRUE, sendToBack = TRUE)) %>%
  addLegend(colors = c("grey60", "#824273"),
            labels = unique(geom1$Creative.industrial), group = "Creative", opacity = 1,
            title = "Creative",
            position = "bottomright") %>%
  # building
  addPolygons(color = ~paletteB(Building.construction.repair),
              fillColor = ~paletteB(Building.construction.repair),
              stroke = TRUE,
              weight = 1,
              opacity = 1,
              fillOpacity = 0.8,
              group = "Building",
              label = paste(
                "Name: ", geom1$Name.of.organis, "<br/>",
                "Sector: ", geom1$Sector, "<br/>",
                "Category: ", geom1$Category.plus, "<br/>",
                "Building/Construction: ", geom1$Building.construction.repair,
                sep="") %>% lapply(htmltools::HTML),
              highlightOptions = highlightOptions(fillOpacity = 0.75, weight = 1, opacity = 1, color = "yellow", bringToFront = TRUE, sendToBack = TRUE)) %>%
  addLegend(colors = c("grey60", "#824273"),
            labels = unique(geom1$Building.construction.repair), group = "Building", opacity = 1,
            title = "Building",
            position = "bottomright") %>%
  # wholesale
  addPolygons(color = ~paletteW(Wholesale.distribution),
              fillColor = ~paletteW(Wholesale.distribution),
              stroke = TRUE,
              weight = 1,
              opacity = 1,
              fillOpacity = 0.8,
              group = "Wholesale",
              label = paste(
                "Name: ", geom1$Name.of.organis, "<br/>",
                "Sector: ", geom1$Sector, "<br/>",
                "Category: ", geom1$Category.plus, "<br/>",
                "Wholesale/Distribution: ", geom1$Wholesale.distribution,
                sep="") %>% lapply(htmltools::HTML),
              highlightOptions = highlightOptions(fillOpacity = 0.75, weight = 1, opacity = 1, color = "yellow", bringToFront = TRUE, sendToBack = TRUE)) %>%
  addLegend(colors = c("grey60", "#ec53a4", "transparent"),
            labels = unique(geom1$Wholesale.distribution), group = "Wholesale", opacity = 1,
            title = "Building",
            position = "bottomright") %>%
  # indu polygons
  addPolylines(data = ipol3,
              color = "#3aa9ab",
              weight = 3,
              opacity = 0.2,
              fill = TRUE,
              fillColor = "#3aa9ab",
              fillOpacity = 0.01,
              #dashArray = "3",
              label = paste(ipol3$Planning_info, "<br/>", ipol3$Layer, 
                            sep="") %>% lapply(htmltools::HTML),
              group = "Industrial Planning",
              highlightOptions = highlightOptions(fillOpacity = 0.2, weight = 1, opacity = 1, color = "yellow", bringToFront = TRUE, sendToBack = TRUE)) %>%
  # layers controls
  addLayersControl(
    overlayGroups = c("Sector","Manufacturing","Repair","Creative","Building","Wholesale","Industrial Planning"),
    baseGroups = c("Street","Satellite"),
    position = "topright",
    options = layersControlOptions(collapsed = FALSE)) %>%
      htmlwidgets::onRender("function() {
            $('.leaflet-control-layers-overlays').prepend('<label style=\"text-align:center\">Map Layers</label>');}") %>%
  hideGroup(c("Manufacturing", "Repair", "Creative","Building","Wholesale","Industrial Planning")) %>%
  addControl("<p>
<img src=\"https://cities.research.londonmet.ac.uk/wp-content/uploads/aad-cities-logo-london-metropolitan-university.jpg\" style=\"width:180px;\"><br>
<b>Southwark Industrial Audit</b><br>
<i class='fas fa-info-circle' style='font-size:20px;color:#2E2E2E'></i>

<a href=\"https://cities.research.londonmet.ac.uk/\" target=\"_blank\">Data & Methodology</a>
<hr></p>", position = "topleft") -> webmap
```

```{r}
#webmap
saveWidget(webmap, here("2022/index.html"), selfcontained = FALSE)
```

# palette Repair
paletteR <- colorFactor(palette = c("grey60", "#658E67"),
                        levels = unique(geom1$Repair), na.color = "transparent")

# palette Creative industrial
paletteC <- colorFactor(palette = c("grey60", "#824273"),
                        levels = unique(geom1$Creative.industrial), na.color = "transparent")

# palette Creative industrial
paletteB <- colorFactor(palette = c("grey60", "#c6610a"),
                        levels = unique(geom1$Building.construction.repair), na.color = "transparent")

# palette Creative industrial
paletteW <- colorFactor(palette = c("grey60", "#ec53a4"),
                        levels = unique(geom1$Wholesale.distribution), na.color = "transparent")



```{r}
geom1 %>%
  st_drop_geometry() %>%
  count(Sector) %>%
  arrange(desc(n))


```


```{r}
geom1 %>%
  st_drop_geometry() %>%
  count(Manufacturing.making)
```


